Figures for 3-D printed oxygen devices

### 2015-01-26 publishing/latex/figures.tex
updated figure1 and outline

\begin{figure}[H]
\includegraphics[scale=0.2]{../presentation-figures/piller-well-render-with-arrows.png} % remove for manuscript submission
\caption{
{\bf CAD rendering of the piller bottom.} The 'Pipe with in a pipe' flow pattern delivers gas to the bottom of each well where it diffuses to the culture.  
}
\label{piller-well-render-figure}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=0.05]{../presentation-figures/24well.JPG} % remove for manuscript submission
\includegraphics[scale=0.05]{../presentation-figures/printed-network.JPG} % remove for manuscript submission
\caption{
{\bf Photographs of the printed device.}  The printed device with membranes adhered. The distribution network is printed completely in resin.
}
\label{device-photos-figure}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
\caption{
{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device. Each 6 well row of the plate can be controlled independently.  
}
\label{oxygen-char-figure}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[scale=0.2]{fig1.png} 
\caption{
{\bf 24-well Insert Device.} A microfluidic network distributes gas flow from one hose barb input to 6 wells.
A 'Pipe with in a pipe' design delivers gas to the bottom of each well where it diffuses to the culture through an adhered PDMS membrane (blue-layer).  
The distribution network width of the channels in the distribution network are such that the flow rates are equalized to each well dependent on the path length.
}
\label{figure1}
\end{figure}

%\begin{figure}[H]
%\includegraphics[scale=0.3]{../presentation-figures/6-well-plot.png} % remove for manuscript submission
%\includegraphics[scale=0.3]{../presentation-figures/24-well-plot.png} % remove for manuscript submission
%\caption{
%{\bf Oxygen Characterization.}  Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device. Each 6 well row of the plate can be controlled independently.  
%}
%\label{oxygen-char-figure}
%\end{figure}
